---
title: "autoHiring"
output: github_document
---

This is a bricks and mortar skeleton  of an idea on how to automatise the production of the documents needed in the hiring process.

The most simple way to generate a form consists in generating a [_parametrized report_](https://rmarkdown.rstudio.com/developer_parameterized_reports.html%23parameter_types%2F#Passing_Parameters) by extracting the data from the excel file and passing it to the `rmarkdown::render()` function as the `params` argument.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      error =TRUE, 
                      eval = FALSE)
```

```{r packs, include = FALSE}
library(dplyr)
library(tidyr)
library(readxl)
library(stringr)
library(anytime)
```

To do this, one can start by extracting the data from the properly formatted Excel sheet. Here, we are only interested in the fields and their. 

```{r extract_data}
person <- 
  readxl::read_excel(path = "data/form2.xlsx", skip = 3) %>% 
  select(`FIELD`,`YOUR DETAILS`) %>% 
  janitor::clean_names() %>% 
  pivot_wider(names_from = field, values_from = your_details) %>% 
  janitor::clean_names()
```

The second step consists in storing the extracted values in a `list`.

```{r}
params_list <-  as.list(person)
```

There's some tweaking to be done with the dates as, when imported from Excel, they provide the 'days since' an origin set in  "1899-12-30". (Just to say that there has to be a more elegant way to do this.) 

```{r}
params_list$date_of_birth <- 
  params_list$date_of_birth %>% 
  as.numeric()%>% as.Date(origin = "1899-12-30")

params_list$date_of_ph_d <- 
  params_list$date_of_ph_d %>% 
  as.numeric() %>% as.Date(origin = "1899-12-30")

params_list$date_of_diploma <- 
  params_list$date_of_diploma%>% 
  as.numeric() %>% as.Date(origin = "1899-12-30")

```


Then, the third step, consists in rendering the CDC and PDE files with the previous list of parameters using `rmarkdown::render()` with `params = params_list`, as in:

```{r render_docs}
rmarkdown::render(
  input = "CDC/README.Rmd", 
  params = params_list
  )

rmarkdown::render(
  input = "PDE/README.Rmd",
  params = params_list
  )
```

- The YAML of the generating documents contain a `params` argument with initial values set to `NA`.

```YAML
---
title: "Proposition d'Engagement"
output: github_document
params:
  last_name         : NA
  first_name        : NA
  avs_number        : NA
  date_of_birth     : NA
  ...
  ...
  
---
```

- The [body of the generating document](PDE/README.Rmd) contains _inline_ placeholders for the values contained in the `params` list, e.g. `params$first_name`, etc. Rendering them on their own produces a document with `NA`'s instead of the data, but through the `params` argument we can fill them in. Check [this example](PDE/README.md) based on [this form](data/form2.xlsx)

The next step consists in small function and testing all the scenarios with a variety of forms. 


