---
title: "autoHiring"
output: github_document
---

This is a bricks and mortar skeleton  of an idea on how to automatise the production of the documents needed in the hiring process.

The most simple way to generate a form consists in generating a [_parametrized report_](https://rmarkdown.rstudio.com/developer_parameterized_reports.html%23parameter_types%2F#Passing_Parameters) by extracting the data from the excel file and passing it to the `rmarkdown::render()` function as the `params` argument.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      error =TRUE, 
                      eval = TRUE)
```

```{r packs, include = FALSE}
library(tidyverse)
library(readxl)
library(janitor)
```

To do this, one can start by extracting the data from the properly formatted Excel sheet. Here, we are only interested in the fields and their. We have the data stored in the form `form_master.xlsx`. 

We can extract the contents of the sheets `CdC` and `Proposition d'engagement`

```{r extract_person_cdc, message = FALSE}
cdc <- 
  readxl::read_excel(path = "data/form_master.xlsx", skip = 1, sheet = 2, col_names = FALSE) %>% 
  janitor::clean_names() %>% 
  pivot_wider(names_from = x1, values_from = x2) %>% 
  janitor::clean_names()

pde <- 
  readxl::read_excel(path = "data/form_master.xlsx", skip = 1, sheet = 3, col_names = FALSE) %>% 
  janitor::clean_names() %>% 
  pivot_wider(names_from = x1, values_from = x2) %>% 
  janitor::clean_names()
```




The second step consists in storing the extracted values in a `list`.

```{r}
params_cdc <-  as.list(cdc)
params_pde <-  as.list(pde)
```

There's some tweaking to be done with the dates as, when imported from Excel, they provide the 'days since' an origin set in  "1899-12-30". (Just to say that there has to be a more elegant way to do this.) 

```{r}
set_date_origin <-  function(x) {
  if(!is.na(x) ){
    if(x==0){
      x <- NA
    } else {
      x <- x %>% 
        as.numeric() %>% 
        as.Date(origin = "1899-12-30")
    }
  }
  x
}

params_cdc$entree_dans_loffice<- 
  set_date_origin(params_cdc$entree_dans_loffice)

params_cdc$a_partir_du <- 
  set_date_origin(params_cdc$a_partir_du) 
  
params_cdc$annee_de_naiss <- 
  set_date_origin(params_cdc$annee_de_naiss)
  
params_pde$engagement_du <- 
  set_date_origin(params_pde$engagement_du)
   
params_pde$engagement_au <- 
  set_date_origin(params_pde$engagement_au)

params_pde$date_de_naissance <- 
  set_date_origin(params_pde$date_de_naissance)

params_pde$date_du_diplome <- 
  set_date_origin(params_pde$date_du_diplome)

params_pde$date_du_doctorat <- 
  set_date_origin(params_pde$date_du_doctorat)
```

Then, the third step, consists in rendering the CDC and PDE files with the previous list of parameters using `rmarkdown::render()` with `params = params_list`, as in:

```{r render_docs}
rmarkdown::render(
  input = "CDC/README.Rmd", 
  params = params_cdc
  )

rmarkdown::render(
  input = "PDE/README.Rmd",
  params = params_pde
  )
```

- The YAML of the generating documents contain a `params` argument with initial values set to `NA`.

```YAML
---
title: "Proposition d'Engagement"
output: github_document
params:
  last_name         : NA
  first_name        : NA
  avs_number        : NA
  date_of_birth     : NA
  ...
  ...
  
---
```

- The [body of the generating document](PDE/README.Rmd) contains _inline_ placeholders for the values contained in the `params` list, e.g. `params$first_name`, etc. Rendering them on their own produces a document with `NA`'s instead of the data, but through the `params` argument we can fill them in. Check [this example](PDE/README.md) based on [this form](data/form2.xlsx)

The next step consists in small function and testing all the scenarios with a variety of forms. 

# Second Approach: One master file - Three sheets

To fill the missing fields, one can think of constructing.  

```{r extract_person, message = FALSE}
person <- 
  readxl::read_excel(path = "data/form_master.xlsx", skip = 3, sheet = 1) %>% 
  janitor::clean_names() %>% 
  select(x1,your_details) %>%
  pivot_wider(names_from = x1, values_from = your_details) %>% 
  janitor::clean_names()

```


