---
title: "autoHiring"
output: github_document
---

This is a bricks and mortar skeleton  of an idea on how to automatise the production of the documents needed in the hiring process.

The most simple way to generate a form consists in generating [_parametrized reports_](https://rmarkdown.rstudio.com/developer_parameterized_reports.html%23parameter_types%2F#Passing_Parameters) by extracting the data from the excel file and passing it to the `rmarkdown::render()` function as the `params` argument.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      error =TRUE, 
                      eval = TRUE, 
                      message = FALSE)
```

```{r packs, include = FALSE}
library(tidyverse)
library(readxl)
library(janitor)
library(htmltools)
```

```{r start_from_scratch, include = FALSE}
rm(list = ls())
```

To do this, one can start by extracting the data from the properly formatted Excel sheet. Here, we are only interested in the sheets 2 and 3, which contain the things    . 
```{r}
extract_and_clean_sheet <- function(file_path, which_sheet){
  readxl::read_xlsx(path = file_path, skip = 1, 
                     sheet = which_sheet, 
                     col_names = FALSE) %>% 
    janitor::clean_names() %>% 
    pivot_wider(names_from = x1, values_from = x2) %>% 
    janitor::clean_names()
}
```

There's some tweaking to be done with the dates as, when imported from Excel, they provide the 'days since' an origin set in  "1899-12-30". (Just to say that there has to be a more elegant way to do this.) For this, we create the function `set_date_origins()`. 

```{r}
set_date_origin <-  function(x) {
  if(!is.na(x) ){
    if(x==0){
      x <- NA
    } else {
      x <- x %>% 
        as.numeric() %>% 
        as.Date(origin = "1899-12-30") %>% 
        format("%d %b %Y")
      x
    }
  }
}
```

With these elements, we construct the function that renders the documents in two formats: `.pdf` and `.md`. 

### `render_cdc()`

```{r}
render_cdc <- function(file_path){
  
  params_cdc <- 
    extract_and_clean_sheet(file_path=file_path, which_sheet = 2) %>% 
    mutate(
      entree_dans_loffice = set_date_origin(entree_dans_loffice), 
      a_partir_du = set_date_origin(a_partir_du), 
      annee_de_naiss = set_date_origin(annee_de_naiss)
      ) %>%
    as.list()
  
  
  rmarkdown::render(
    input = "CDC/README.Rmd", 
    params = params_cdc, 
    output_format = c("pdf_document", "github_document")
  )
  
  rmarkdown::render(
    input = "CDC/index.Rmd", 
    params = params_cdc
    )
  
  # params_cdc
}
```

### `render_pde()`

```{r}
render_pde <- function(file_path){
  
  params_pde <- 
    extract_and_clean_sheet(file_path=file_path, which_sheet =3) %>%
    mutate(
      engagement_du     = set_date_origin(engagement_du),
      engagement_au     = set_date_origin(engagement_au), 
      date_de_naissance = set_date_origin(date_de_naissance), 
      date_du_diplome   = set_date_origin(date_du_diplome),
      date_du_doctorat  = set_date_origin(date_du_doctorat) 
    ) %>% 
    as.list()
  
  rmarkdown::render(
    input = "PDE/README.Rmd", 
    params = params_pde, 
    output_format = c("pdf_document", "github_document")
  )
  rmarkdown::render(
    input = "PDE/index.Rmd", 
    params = params_pde
    )
  # params_pde
}
```

- We set the `file_path`

```{r, warings = FALSE}
file_path  <- "data/EPFL Extension School-Personal Details-MASTER-for Daniel-02SEP2020.xlsx"
```

- Render the  _Cahier des charges_ with `render_cdc()`
```{r, warnings = FALSE}
render_cdc(file_path)
```

- And the _Proposition d'Engagement_ with `render_pde()`
```{r, warnings = FALSE}
render_pde(file_path)
```

### A word on the principle

- The basic principle consists in having a YAML of the generating documents contain a `params` argument with initial values set to `NA`.

```YAML
---
title: "Proposition d'Engagement"
output: github_document
params:
  last_name         : NA
  first_name        : NA
  avs_number        : NA
  date_of_birth     : NA
  ...
  ...
  
---
```

- The [body of the generating document](PDE/README.Rmd) contains _inline_ placeholders for the values contained in the `params` list, e.g. `params$first_name`, etc. Rendering them on their own produces a document with `NA`'s instead of the data, but through the `params` argument we can fill them in. Check [this example](PDE/README.md) based on [this form](data/form_master.xlsx)

The next step consists in small function and testing all the scenarios with a variety of forms. 